Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers

### 2021-07-20 analysis/report/effectiveness_report.Rmd
output rds effects; redo report plots

print_plots <- function(outcome, outcome_descr){
  km_image <- here("output", "descriptive", "km", glue("plot_survival_ci_{outcome}.png"))
  calendar_image <- here("output", outcome, "calendar", glue("effect_plot_cox.png"))
  timesincevax_image <- here("output", outcome, "timesincevax", glue("effect_plot_cox.png"))

@@

  calendar_plot <- read_rds(here("output", outcome, "calendar", glue("effect_plot_cox.rds"))) + 
    labs(title=NULL)+
    coord_cartesian(ylim=c(0.25,4))+
    theme(text = element_text(size=10))

  timesincevax_plot <- read_rds(here("output", outcome, "timesincevax", glue("effect_plot_cox.rds"))) + 
    labs(title=NULL)+
    coord_cartesian(ylim=c(0.25,4))+
    theme(text = element_text(size=10))

  #cat(glue("### {outcome_descr}"), "  \n")

  effects_plot <- wrap_plots(calendar_plot, timesincevax_plot, nrow=1)#, guides='collect')

>>>>

print_plots <- function(outcome, outcome_descr){
  km_image <- here("output", "descriptive", "km", glue("plot_survival_ci_{outcome}.png"))
  calendar_image <- here("output", outcome, "calendar", glue("effect_plot.png"))
  timesincevax_image <- here("output", outcome, "timesincevax", glue("effect_plot.png"))

@@

  calendar_effects <- read_rds(here("output", outcome, "calendar", glue("effect_estimates.rds"))) %>%
    mutate(timescale = "Calendar time")
  timesincevax_effects <- read_rds(here("output", outcome, "timesincevax", glue("effect_estimates.rds"))) %>%
    mutate(timescale = "Vaccinated time")

  effects <- bind_rows(calendar_effects, timesincevax_effects)

  effects_plot <-
    ggplot(data = effects) +
    geom_point(aes(y=estimate, x=term_midpoint, colour=model_name), position = position_dodge(width = 1.8))+
    geom_linerange(aes(ymin=conf.low, ymax=conf.high, x=term_midpoint, colour=model_name), position = position_dodge(width = 1.8))+
    geom_hline(aes(yintercept=1), colour='grey')+
    facet_grid(cols=vars(timescale))+
    scale_x_continuous(breaks=unique(effects$term_left), limits=c(min(effects$term_left), max(effects$term_right)+1), expand = c(0, 0))+
    scale_y_log10(
    breaks=c(0.1, 0.25, 0.33, 0.5, 0.75, 1, 1.33, 2, 3, 4, 10)
    #sec.axis = dup_axis(name="favours\n<- BNT162b2 / ChAdOx1 ->", breaks = NULL)
  )+
    scale_colour_brewer(type="qual", palette="Set2", guide=guide_legend(ncol=2))+
    labs(
      y="Hazard ratio\nChAdOx1 / BNT162b2",
      x="Days since vaccination",
      colour=NULL
     ) +
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),

      panel.grid.minor.x = element_blank(),
      panel.grid.minor.y = element_blank(),
      strip.background = element_blank(),
      strip.placement = "outside",
      strip.text.y.left = element_text(angle = 0),

      panel.spacing = unit(0.8, "lines"),

      plot.title = element_text(hjust = 0),
      plot.title.position = "plot",
      plot.caption.position = "plot",
      plot.caption = element_text(hjust = 0, face= "italic"),

      legend.position = "bottom"
     ) +
   NULL

  # 
  # calendar_plot <- read_rds(here("output", outcome, "calendar", glue("effect_plot.rds"))) + 
  #   labs(title=NULL)+
  #   coord_cartesian(ylim=c(0.25,4))+
  #   theme(text = element_text(size=10))
  # 
  # timesincevax_plot <- read_rds(here("output", outcome, "timesincevax", glue("effect_plot.rds"))) + 
  #   labs(title=NULL)+
  #   coord_cartesian(ylim=c(0.25,4))+
  #   theme(text = element_text(size=10))
  # 
  cat(glue("### {outcome_descr}"), "  \n")

  #effects_plot <- wrap_plots(calendar_plot, timesincevax_plot, nrow=1)#, guides='collect')
